Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-22 03-analysis.Rmd
Estimate model with no SE

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 6,
  cores = 6,
  threads = 2,
  iter = 1500, 
  warmup = 1000,
  refresh = 10,
  adapt_delta = .95, 
  max_treedepth = 11
)

@@

# Regression coefficients
p <- prior(normal(0, .5), class = b, resp = val) +
  prior(normal(0, 1), class = b, coef = sex1, resp = val) +
  # Standard deviations
  prior(
    student_t(7, 0, .5), 
    class = sd, resp = val, group = region
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, resp = val, group = region, coef = Intercept
  ) +
  prior(
    student_t(7, 0, .5), 
    class = sd, resp = val, group = country
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, resp = val, group = country, coef = Intercept
  ) +
  # Correlations
  prior(lkj(2), class = cor, group = country) +
  prior(lkj(2), class = cor, group = region)

# Compile model separately for each outcome to give independent default priors
fits_1c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1c + set_rescor(FALSE), 
        data = cur_data_all(),
        prior = p,
        sample_prior = "yes",
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1c-{cur_group()}")
      )
    )
  )

```

@@

# Regression coefficients
p <- prior(normal(0, .5), class = b) +
  prior(normal(0, 1), class = b, coef = sex1) +
  # Standard deviations
  prior(
    student_t(7, 0, .5), class = sd, group = region
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, group = country, coef = Intercept
  ) +
  prior(
    student_t(7, 0, .5), class = sd, group = region
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, resp = val, group = country, coef = Intercept
  ) +
  # Correlations
  prior(lkj(2), class = cor, group = country) +
  prior(lkj(2), class = cor, group = region)

# Compile model separately for each outcome to give independent default priors
fits_2c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_2c, 
        data = cur_data_all(),
        prior = p,
        sample_prior = "yes",
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2c-{cur_group()}")
      )
    )
  )
```

>>>>

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 4,
  cores = 4,
  threads = 3,
  iter = 1500, 
  warmup = 750,
  refresh = 10,
  adapt_delta = .90, 
  max_treedepth = 10
)

@@

# Compile model separately for each outcome to give independent default priors
fits_1c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1c + set_rescor(FALSE), 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1c-{cur_group()}")
      )
    )
  )

bf_1c_no_se <- bf(
  val ~ 
    year * sex + year * age + 
    (year * sex + year * age |c| country) +
    (year * sex + year * age |r| region),
  family = gaussian()
)

# Compile model separately for each outcome to give independent default priors
fits_1c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit_no_se = list(
      brm(
        formula = bf_itu + bf_1c_no_se + set_rescor(FALSE), 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1c-no-se-{cur_group()}")
      )
    )
  )
```

@@

bf_2c_no_se <- bf(
  val ~ 
    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
  family = gaussian()
)

# Compile model separately for each outcome to give independent default priors
fits_2c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_2c, 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2c-{cur_group()}")
      )
    )
  )

fits_2c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit_no_se = list(
      brm(
        formula = bf_2c_no_se, 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2c-no-se-{cur_group()}")
      )
    )
  )
```
